Topic and tone of political news articles in German online media.

### 2018-04-15 paper/docs/04_Modelresults_50.Rmd
push current paper status

---
title: "Whats reported in the news?"
subtitle: ""
author: "Franziska Löw"
date: ""
output: 
  html_document:
    theme: "lumen"
    highlight: "tango"
    code_folding: show
    self_contained: true
---

@@

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[8], alpha = 0.8) +
  labs(x="", y="Number of articles") +
  theme(
    axis.text = element_text(size = 6),
      legend.position   = "none"
    )

},
filename = "../figs/bar.png", device = "png", 
width = 6, height = 4,
        dpi = 600)
```

![plot1](../figs/bar.png)
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs)) +
  geom_line(color=col[3]) +
  geom_vline(aes(xintercept=as.Date("2017-09-24")),
             linetype = 2, color=col[5]) +
  geom_vline(aes(xintercept=as.Date("2017-11-19")),
             linetype = 2, color=col[5]) +
  scale_color_manual(values = col) +
  labs(x="", y="number of articles",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      legend.position   = "none",
      axis.title.x      = element_blank(),
      axis.text       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 6, height = 4,
dpi = 600
)

@@

<img src="../figs/wordcloud_Bild.de.png", width = "49%" title="Bild.de">
<img src="../figs/wordcloud_DIE WELT.png", width = "49%" title="DIE WELT">
<img src="../figs/wordcloud_FOCUS ONLINE.png", width = "49%" title="FOCUS ONLINE">
<img src="../figs/wordcloud_SPIEGEL ONLINE.png", width = "49%" title="SPIEGEL ONLINE">
<img src="../figs/wordcloud_stern.de.png", width = "49%" title="Stern.de">
<img src="../figs/wordcloud_Tagesschau.de.png", width = "49%" title="Tagesschau.de">
<img src="../figs/wordcloud_ZEIT ONLINE.png", width = "49%" title="ZEIT ONLINE">

@@

<!-- <img src="../figs/radarchart_2017-06.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-07.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-09.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-10.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-11.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-12.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2018-01.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2018-02.png", width = "49%"> -->

@@

```{r}
polls_monthly <- polls %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(!party %in% c("Piraten", "Sonstige")) %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val) %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  filter(yearmonth < as.Date("2018-03-01")) %>%
  mutate(AfD = normalize_data(AfD),
         FDP = normalize_data(FDP),
         Grüne = normalize_data(Grüne),
         Linke = normalize_data(Linke),
         SPD = normalize_data(SPD),
         Union = normalize_data(Union))

polls_monthly %>%
  gather(key = party, value = poll, AfD:Union) %>%
  ggplot(aes(yearmonth, poll, color = party)) +
  geom_line() +
  scale_color_manual(values =  c("deepskyblue", "gold", "limegreen", "deeppink", "red", "black")) +
  labs(x="", y="", title = "Survey Value", 
       subtitle = "weekly", color = "") +
  geom_vline(xintercept = as.Date("2017-09-24"), 
             linetype = 2, color = col[3]) +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%b", tz="CET")) +
    theme(axis.text.x = element_text(size = 10))
```

@@

@@

##### 3.1.2. By Media
```{r eval=FALSE, include=FALSE}
for (i in unique(group2$site)) {

@@

<img src="../figs/corrplot_Bild.de.png", width = "49%">
<img src="../figs/corrplot_DIE WELT.png", width = "49%">
<img src="../figs/corrplot_FOCUS ONLINE.png", width = "49%">
<img src="../figs/corrplot_SPIEGEL ONLINE.png", width = "49%">
<img src="../figs/corrplot_stern.de.png", width = "49%">
<img src="../figs/corrplot_Tagesschau.de.png", width = "49%">
<img src="../figs/corrplot_ZEIT ONLINE.png", width = "49%">

#### 3.2. Graphical analysis

For each party, we plot the topics that most strongly correlate with the poll data.

```{r}
plot_Poll_Sent <- function(topics_number, party_str, color_str) {

@@

##### 3.2.1. CDU
```{r fig.height=12, fig.width=10}
topic_number <- c(10,13,23,26)

@@

#### SPD
```{r fig.height=12, fig.width=10}
topic_number <- c(1,17,22)

@@

##### 3.2.3. AfD
```{r fig.height=12, fig.width=10}
topic_number <- c(17,22, 30)

@@

#### FDP
```{r fig.height=12, fig.width=10}
topic_number <- c(23,26,27)

@@

#### Grüne
```{r fig.height=12, fig.width=10}
topic_number <- c(26,27,17)

@@

#### DIE LINKE
```{r fig.height=12, fig.width=10}
topic_number <- c(1,17,22)

>>>>

---
title: "Topic and tone of political news articles in German online media."
subtitle: ""
author: "Franziska Löw"
date: "April 2018"
output: 
  html_document:
    theme: "lumen"
    highlight: "tango"
    code_folding: show
    self_contained: true
---

@@

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[8], alpha = 0.8) +
  labs(x="", y="Number of articles") +
  theme(
    axis.text.x = element_text(size = 9),
      legend.position   = "none"
    )

},
filename = "../figs/bar.png", device = "png", 
width = 7, height = 4,
        dpi = 600)
```

![plot1](../figs/bar.png)
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs)) +
  geom_line(color=col[3]) +
  geom_vline(aes(xintercept=as.Date("2017-09-24")),
             linetype = 2, color=col[5]) +
  geom_vline(aes(xintercept=as.Date("2017-11-19")),
             linetype = 2, color=col[5]) +
  scale_color_manual(values = col) +
  labs(x="", y="Number of Articles",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      legend.position   = "none",
      axis.title.x      = element_blank(),
      axis.text       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 6, height = 4,
dpi = 600
)

@@

<img src="../figs/wordcloud_Bild.png", width = "49%" title="Bild.de">
<img src="../figs/wordcloud_DIEWELT.png", width = "49%" title="DIE WELT">
<img src="../figs/wordcloud_FOCUSONLINE.png", width = "49%" title="FOCUS ONLINE">
<img src="../figs/wordcloud_SPIEGELONLINE.png", width = "49%" title="SPIEGEL ONLINE">
<img src="../figs/wordcloud_stern.png", width = "49%" title="Stern.de">
<img src="../figs/wordcloud_Tagesschau.png", width = "49%" title="Tagesschau.de">
<img src="../figs/wordcloud_ZEITONLINE.png", width = "49%" title="ZEIT ONLINE">

@@

@@

```{r}
polls_monthly <- polls %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(!party %in% c("Piraten", "Sonstige")) %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val) %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  filter(yearmonth < as.Date("2018-03-01")) %>%
  mutate(AfD = normalize_data(AfD),
         FDP = normalize_data(FDP),
         Grüne = normalize_data(Grüne),
         Linke = normalize_data(Linke),
         SPD = normalize_data(SPD),
         Union = normalize_data(Union))
```

@@

![Cross-correlation 2](../figs/ccf2.png)

@@

```{r eval=FALSE, include=FALSE}
for (i in unique(group2$site)) {

@@

<!-- <img src="../figs/corrplot_Bild.de.png", width = "49%"> -->
<!-- <img src="../figs/corrplot_DIE WELT.png", width = "49%"> -->
<!-- <img src="../figs/corrplot_FOCUS ONLINE.png", width = "49%"> -->
<!-- <img src="../figs/corrplot_SPIEGEL ONLINE.png", width = "49%"> -->
<!-- <img src="../figs/corrplot_stern.de.png", width = "49%"> -->
<!-- <img src="../figs/corrplot_Tagesschau.de.png", width = "49%"> -->
<!-- <img src="../figs/corrplot_ZEIT ONLINE.png", width = "49%"> -->

<!-- #### 3.2. Graphical analysis -->

<!-- For each party, we plot the topics that most strongly correlate with the poll data.  -->

```{r eval=FALSE, include=FALSE}
plot_Poll_Sent <- function(topics_number, party_str, color_str) {

@@

##### 3.2.1. CDU
```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
topic_number <- c(10,13,23,26)

@@

#### SPD
```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
topic_number <- c(1,17,22)

@@

##### 3.2.3. AfD
```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
topic_number <- c(17,22, 30)

@@

#### FDP
```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
topic_number <- c(23,26,27)

@@

#### Grüne
```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
topic_number <- c(26,27,17)

@@

#### DIE LINKE
```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
topic_number <- c(1,17,22)
